Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-28 research_proposal/research_proposal.qmd
write up background knowledge

$$
\bm{y}_t = \bm{S} \bm{b}_t,
$$

where $\bm{S}$ is a summing matrix of order $n /times n_b$ which aggregates the bottom-level series $\bm{b}_t$ ($n_b$-vector) to the series at aggregation levels above. The $n$-vector $\bm{y}_t$ contains all observations at time $t$.

>>>>

$$
\boldsymbol{y}_t = \boldsymbol{S} \boldsymbol{b}_t,
$$ {#eq-1}

where $\boldsymbol{S}$ is a summing matrix of order $n \times n_b$ which aggregates the bottom-level series $\boldsymbol{b}_t$ ($n_b$-vector) to the series at aggregation levels above. The $n$-vector $\boldsymbol{y}_t$ contains all observations at time $t$.

The example summing matrix $\boldsymbol{S}$ for the tree structure in *Figure 1* is:

$$
\boldsymbol{S} = 
\left[
\begin{array}{cccc}
1 & 1 & 1 & 1 \\
1 & 1 & 0 & 0 \\
0 & 0 & 1 & 1 \\
\multicolumn{4}{c}{\boldsymbol{I_n}}
\end{array}
\right],
$$

The MinT method is a popular choice for estimating $\boldsymbol{G}_h$, as it minimizes the trace of the covariance matrix of the forecast errors, which is a measure of the uncertainty in the forecasts. The MinT method requires an estimate of the covariance matrix of the base forecast errors, which is typically obtained using a shrinkage estimator. However, this approach has limitations, as it may not fully capture the structure of the data.
